Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-08 sas2015/content/example.tex
removing stuff

Figure~\ref{list:ccexample} shows a small Java program that we will use to illustrate
how our technique improves the precision of a simple taint analysis. The program
declares a class \code{A} with a subclass \code{B},  where \code{A} defines methods 
\code{foo()} and \code{bar()} that are overridden in \code{B}.  In order to keep the 
example small and self-contained, it is assumed  that secret values are created by 
an unspecified function \code{secret()}, which is called in method \code{A.foo()} on 
line~\ref{line:Afoo}. Furthermore, it is assumed that any write to the standard output 
stream via calls \code{System.out.println()} such as the one in method \code{B.bar()} 
on line~\ref{line:Bbar} is a security-sensitive operation. Depending on the number of 
arguments passed to the program, the \code{main()} method of the example program creates 
either an \code{A}-object or a \code{B}-object on line~\ref{line:createObject}. The 
program then calls \code{foo()} on this object on line~\ref{line:callfoo}, which is 
followed by a call to \code{bar()} on the same object on line~\ref{line:callbar}.

The specific question that we would like to answer for the example program of
Figure~\ref{list:ccexample} is the following: Is it possible for the untrusted value 
that is read on line~\ref{line:Afoo} to flow to the print statement on line~\ref{line:Bbar}? 
%
To determine whether such a flow of tainted data is possible, consider the control-flow
supergraph for the example program that is shown in Figure~\ref{fig:examplesupergraph}.
 The nodes in this graph correspond to statements, method entry points (start nodes) and 
method exit points (end nodes). Note that for each method call, the graph contains a 
distinct call-node and a return-node. Edges in the graph reflect intraprocedural control flow, 
flow of control from a caller to a callee (edges from call-nodes to start-nodes), or
flow of control from a callee back to a caller (edges from end-nodes to return-nodes).

>>>>

Figure~\ref{list:ccexample} shows a small Java program that we will use to illustrate
how our technique improves the precision of a simple taint analysis. The program
declares a class \code{A} with a subclass \code{B},  where \code{A} defines methods 
\code{foo()} and \code{bar()} that are overridden in \code{B}.  
%In order to keep the example small and self-contained, 
It is assumed  that secret values are created by 
an unspecified function \code{secret()}, which is called in method \code{A.foo()}%
%  on line~\ref{line:Afoo}
. Furthermore, it is assumed that any write to the standard output 
stream via calls \code{System.out.println()} such as the one in method \code{B.bar()} 
%on line~\ref{line:Bbar} 
is a security-sensitive operation. Depending on the number of 
arguments passed to the program, the \code{main()} method of the example program creates 
either an \code{A}-object or a \code{B}-object%
%on line~\ref{line:createObject}
. The 
program then calls \code{foo()} on this object
on line~\ref{line:callfoo}, which is 
followed by a call to \code{bar()} on the same object%
%on line~\ref{line:callbar}
.

The specific question that we would like to answer for the example program of
Figure~\ref{list:ccexample} is the following: Is it possible for the untrusted value 
that is read on line~\ref{line:Afoo} to flow to the print statement% %on line~\ref{line:Bbar}
?
To determine whether such a flow of tainted data is possible, consider the control-flow
supergraph for the example program that is shown in Figure~\ref{fig:examplesupergraph}.
 The nodes in this graph correspond to statements, method entry points (start nodes) and 
method exit points (end nodes). Note that for each method call, the graph contains a 
distinct call-node and a return-node. Edges in the graph reflect intraprocedural control flow, 
flow of control from a caller to a callee (edges from call-nodes to start-nodes), or
flow of control from a callee back to a caller (edges from end-nodes to return-nodes).
